---
fontsize: 12pt
geometry: margin=0.50in
subparagraph: yes
title: CGD samples
date: September 2019
author: John K. Everett
indent: false
header-includes:
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}
   - \usepackage{pdfpages}
output:
  pdf_document:
    toc: false
    keep_tex: yes
    latex_engine: xelatex
---
```{r echo = FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(png)
library(grid)
library(ggplot2)
library(dplyr)
library(vegan)
library(RColorBrewer)
library(gridExtra)
load('data/report.RData')
ppNum <- function (n) format(n, big.mark = ",", scientific = FALSE, trim = TRUE)
Y1.PBMC <- dplyr::filter(intSites, timePoint == 'Y1' & cellType == 'PBMC')

Y1.PBMC.counts <- subset(intSites,  timePoint == 'Y1' & cellType == 'PBMC') %>% 
  group_by(patient) %>% 
  summarise(sites = n_distinct(posid),
            chaoCells = round(estimateR(estAbund, index='chao')[2], 0)) %>%
  ungroup()

```

**Project interface**  

Individual patient reports and a detailed account of received sample can be found via this 
([Link](http://bushmanlab.org/data/export/projects/gtVISA/CGD)).

\vspace{0.5cm}
**Basic stats**  
Average number of integrations per subject in PBMC at Y1: `r round(mean(Y1.PBMC.counts$sites))`  
Average number of sampled cells (Chao1 estimate) per subject in PBMC at Y1: `r ppNum(round(mean(Y1.PBMC.counts$chaoCells)))`  
Max. rel. abund. of clones in PBMC at Y1: `r sprintf("%.2f%%", max(Y1.PBMC$relAbund))`  
Max. rel. abund. of clones near SETBP1, PRDM16 and MECOM in PBMC at Y1: `r sprintf("%.2f%%", max(subset(Y1.PBMC, nearestFeature %in% c('SETBP1', 'PRDM16', 'MECOM'))$relAbund))`    
Max. rel. abund. of clones in PBMC (all time points): `r sprintf("%.2f%%", max(subset(intSites, cellType == 'PBMC')$relAbund))`  

\vspace{0.5cm}

**Observed integrations**  
Bar graph format  

\vspace{1.0cm}


```{r, echo = FALSE, message = FALSE, fig.width=8, fig.height=5.5}
obsIntSites2
```

\newpage

**Observerd integrations**  
log10 scale line plot format.  

\vspace{0.5cm}


```{r, echo = FALSE, message = FALSE, fig.width=7, fig.height=9}
obsIntSites 
```

\newpage

**Integrations near previously reported bad actors**  

\vspace{1.0cm}


```{r, echo = FALSE, message = FALSE, fig.width=8, fig.height=9, warning=FALSE}
badActorPlot 
```

\newpage

**Neutrophils heat maps**  

\vspace{1.0cm}

```{r, echo = FALSE, fig.height = 10}
grid.arrange(gA, gB, gC, gD, legend, ncol=1) 
```

\newpage

**Neutrophils heat maps**  (cont.)  

\vspace{1.0cm}

```{r, echo = FALSE, fig.height = 8}
grid.arrange(gE, gF, gG, legend, ncol=1)
```

\newpage

**Sample and data collection summary**  

\vspace{0.5cm}

```{r, echo = FALSE}
kable(summaryTable, "latex", longtable = T, booktabs = T, linesep = '', align = 'lllclllllll') %>% kable_styling(font_size = 9, latex_options = c("repeat_header"))
```


