---
fontsize: 12pt
geometry: margin=0.50in
subparagraph: yes
title: CGD samples
date: September 2019
author: John K. Everett
indent: false
header-includes:
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}
   - \usepackage{pdfpages}
output:
  pdf_document:
    toc: false
    keep_tex: no
    latex_engine: xelatex
---
```{r echo = FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(png)
library(grid)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(gridExtra)
load('report.RData')
ppNum <- function (n) format(n, big.mark = ",", scientific = FALSE, trim = TRUE)
```

**Project interface**  

Individual patient reports and a detailed account of received sample can be found via this 
([Link](http://bushmanlab.org/data/export/projects/gtVISA/CGD)).

\vspace{1.0cm}

**Observed integrations**  
Bar graph format  

\vspace{1.0cm}


```{r, echo = FALSE, message = FALSE, fig.width=8, fig.height=6.5}
obsIntSites2
```

\newpage

**Observerd integrations**  
log10 scale line plot format.  

\vspace{0.5cm}


```{r, echo = FALSE, message = FALSE, fig.width=7, fig.height=9}
obsIntSites 
```

\newpage

**Integrations near previously reported bad actors**  

\vspace{1.0cm}


```{r, echo = FALSE, message = FALSE, fig.width=8, fig.height=9, warning=FALSE}
badActorPlot 
```

\newpage

**Neutrophils heat maps**  

\vspace{1.0cm}

```{r, echo = FALSE, fig.height = 10}
grid.arrange(gA, gB, gC, gD, legend, ncol=1) 
```

\newpage

**Neutrophils heat maps**  (cont.)  

\vspace{1.0cm}

```{r, echo = FALSE, fig.height = 8}
grid.arrange(gE, gF, gG, legend, ncol=1)
```

\newpage

**Sample and data collection summary**  

\vspace{0.5cm}

```{r, echo = FALSE}
kable(summaryTable, "latex", longtable = T, booktabs = T, linesep = '', align = 'lllclllllll') %>% kable_styling(font_size = 7, latex_options = c("repeat_header"))
```


